---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `shinyap`

<!-- badges: start -->
<!-- badges: end -->

The goal of `shinyap` is to provide easy access to the apps in the [Shiny App-Packages](https://mjfrigaard.github.io/shiny-app-pkgs/) book.

## Installation

You can install the development version of `shinyap` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mjfrigaard/shinyap")
```

```{r}
library(shinyap)
```

## Git/GitHub configuration

`shinyap` uses the [`gert` package](https://docs.ropensci.org/gert/) for Git/GitHub management (and assumes authentication was done automatically using the `credentials` package).[^credentials]

[^credentials]: Check out the documentation for the [`credentials` package](https://docs.ropensci.org/credentials/articles/intro.html)


## Available app-packages

To see a list of the available app-packages in `shinyap`, use `list_apps()`[^all-apps]

[^all-apps]: Each of the apps in `shinyap` have a corresponding branch in the [moviesApp repo](https://github.com/mjfrigaard/moviesApp/branches/all).


```{r list_apps, eval=FALSE}
list_apps()
```


## Clone an app

```{r clone_app, eval=FALSE}
clone_app("app name")
```

## Launch an app (or app package)

```{r launch_app, eval=FALSE}
launch_app("app name")
```

## Update an app (or app-package)

To get the most recent version of an app-package, use `update_app()`

```{r update_app, eval=FALSE}
update_app("app name")
```

`update_app()` 
